Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-09 paper/paper.tex
added hmm
expanded names of tests

The other comparison must be made between Anglican and another
probabilistic programming environment. WebPPL~\cite{GS15} is
similar to Anglican in expressivity.  WebPPL runs on top of
\href{http://v8project.blogspot.com/}{V8}, a high performance
JavaScript engine featuring a native compiler.
Table~\ref{tbl:webppl} shows results for a few models from
\href{https://github.com/probmods/webppl}{WebPPL distribution},
as well as from Anglican test suite. For the comparison, we
re-implemented WebPPL models in Anglican, and Anglican models in
WebPPL, following as close as possible the original
implementations, and run the same inference algorithm (called
MCMC in WebPPL, LMH in Anglican) with the same number of
iterations. Anglican outperforms WebPPL on all models. This can
be attributed both to a better transformed representation of
probabilistic programs and to more efficient architecture of the
inference engine.
\begin{table}
    \centering
	\begin{tabular}{r|S[table-format=2.2]|S[table-format=2.2]}
		{\bf model}  & {\bf Anglican} & {\bf WebPPL} \\ \hline
		LDA & 22. & 31. \\ 
		\shortstack{Linear regression}  & 0. & 0. \\
		\shortstack{Logistic regression} & 6.2 & 9.4 \\
		\shortstack{Multivariate regression} & 0. & 0. \\
		\shortstack{Simple branching} & 0. & 0.
    \end{tabular}

>>>>

The other comparison must be made between Anglican and another
probabilistic programming environment. WebPPL~\cite{GS15} is
similar to Anglican in expressivity.  WebPPL runs on top of
\href{http://v8project.blogspot.com/}{V8}, a high performance
JavaScript engine featuring a native compiler.
Table~\ref{tbl:webppl} shows results for a few models from
\href{https://github.com/probmods/webppl}{WebPPL distribution},
as well as from
\href{https://bitbucket.org/probprog/anglican}{Anglican test
suite}. For the comparison, we re-implemented WebPPL models in
Anglican, and Anglican models in WebPPL, following as close as
possible the original implementations, and run the same
inference algorithm (called MCMC in WebPPL, LMH in Anglican)
with the same number of iterations. Anglican outperforms WebPPL
on all models. This can be attributed both to a better
transformed representation of probabilistic programs and to more
efficient architecture of the inference engine.
\begin{table}
    \centering
	\begin{tabular}{r|S[table-format=2.2]|S[table-format=2.2]}
		{\bf model}  & {\bf Anglican} & {\bf WebPPL} \\ \hline
		Latent Dirichlet allocation & 22. & 31. \\ 
		Linear regression  & 0. & 0. \\
		Logistic regression & 6.2 & 9.4 \\
		Multivariate regression & 0. & 0. \\
		Simple branching & 0. & 0. \\
		Hidden Markov model & 0. & 0.
    \end{tabular}
